Who does big team science?

### 2022-09-09 04.manuscript_scopus.Rmd
updated with no typos

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            : papaja::apa6_pdf
---

@@

However, the success and interest in the large-scale reproducibility
projects [@opensciencecollaboration2015; @10.7554/eLife.71601], paired
with the meta-scienctific publications focusing on researcher practices
and incentive structures [@silberzahn2018many; @john2012] led to a
change in journal guidelines and incentives for researchers interested
in participating in large-scale replication studies [@grahe2014;
@kidwell2016; @nosek2015; @mayo-wilson2021]. For example, the support
for Registered Reports, papers accepted before the data has been
collected [@nosek2014; @stewart2020], and entire sub-sections of
journals devoted to only replication studies (e.g., *Nature, Royal
Society Open Science, Advances in Methods and Practices in Psychological
Science*) has allowed researchers to invest in projects that they know
should be published when the project is complete. Further, the
implementation of the Transparency and Openness Guidelines [@nosek2015]
and the Contributor Role Taxonomy (CRediT) system [@allen2019] have
pushed journals and researchers to promote more open, inclusive
publication practices.

>>>>

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            : papaja::apa6_docx
---

@@

However, the success and interest in the large-scale reproducibility
projects [@opensciencecollaboration2015; @10.7554/eLife.71601], paired
with the meta-scientific publications focusing on researcher practices
and incentive structures [@silberzahn2018many; @john2012] led to a
change in journal guidelines and incentives for researchers interested
in participating in large-scale replication studies [@grahe2014;
@kidwell2016; @nosek2015; @mayo-wilson2021]. For example, the support
for Registered Reports, papers accepted before the data has been
collected [@nosek2014; @stewart2020], and entire sub-sections of
journals devoted to only replication studies (e.g., *Nature, Royal
Society Open Science, Advances in Methods and Practices in Psychological
Science*) has allowed researchers to invest in projects that they know
should be published when the project is complete. Further, the
implementation of the Transparency and Openness Guidelines [@nosek2015]
and the Contributor Role Taxonomy (CRediT) system [@allen2019] have
pushed journals and researchers to promote more open, inclusive
publication practices.

### 2022-09-09 04.manuscript_scopus.tex
updated with no typos

However, the success and interest in the large-scale reproducibility
projects (Errington et al., 2021; Open Science Collaboration, 2015), paired
with the meta-scienctific publications focusing on researcher practices
and incentive structures (John et al., 2012; Silberzahn et al., 2018) led to a
change in journal guidelines and incentives for researchers interested
in participating in large-scale replication studies (Grahe, 2014; Kidwell et al., 2016; Mayo-Wilson et al., 2021; Nosek et al., 2015). For example, the support
for Registered Reports, papers accepted before the data has been
collected (Nosek \& Lakens, 2014a; S. Stewart et al., 2020), and entire sub-sections of
journals devoted to only replication studies (e.g., \emph{Nature, Royal
Society Open Science, Advances in Methods and Practices in Psychological
Science}) has allowed researchers to invest in projects that they know
should be published when the project is complete. Further, the
implementation of the Transparency and Openness Guidelines (Nosek et al., 2015)
and the Contributor Role Taxonomy (CRediT) system (Allen et al., 2019) have
pushed journals and researchers to promote more open, inclusive
publication practices.

>>>>

However, the success and interest in the large-scale reproducibility
projects (Errington et al., 2021; Open Science Collaboration, 2015), paired
with the meta-scientific publications focusing on researcher practices
and incentive structures (John et al., 2012; Silberzahn et al., 2018) led to a
change in journal guidelines and incentives for researchers interested
in participating in large-scale replication studies (Grahe, 2014; Kidwell et al., 2016; Mayo-Wilson et al., 2021; Nosek et al., 2015). For example, the support
for Registered Reports, papers accepted before the data has been
collected (Nosek \& Lakens, 2014a; S. Stewart et al., 2020), and entire sub-sections of
journals devoted to only replication studies (e.g., \emph{Nature, Royal
Society Open Science, Advances in Methods and Practices in Psychological
Science}) has allowed researchers to invest in projects that they know
should be published when the project is complete. Further, the
implementation of the Transparency and Openness Guidelines (Nosek et al., 2015)
and the Contributor Role Taxonomy (CRediT) system (Allen et al., 2019) have
pushed journals and researchers to promote more open, inclusive
publication practices.
